---
title: "Intro to R for Epidemiologists"
subtitle: Lab 12
author: "Your name"
date: "Thursday, April 9, 2015"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    theme: cosmo
    toc: true
---

```{r knitr_options, echo = F, warning = F, message = F}
# Load libraries
library(ggplot2)
library(dplyr)
library(knitr)

# Set global options
opts_chunk$set(echo = F, eval = T, message = F, warning = F, results = 'asis')
```

For this lab, you will use R Markdown and `knitr` to recreate this report.  Your lab only needs to include the header (above this paragraph) and the numbered sections below starting with *Introduction*.  You will need the `diabetes` dataset from lab 8 and the `tab_diab` object from Homework 1.  


Instructions:

1. Create a header with title, subtitle, author, and date
2. Change the options for the html_document output to allow figure captions, numbered sections, and a table of contents.  Additionally, change the theme to cosmo.
3. In a code chunk, set global `knitr` options and load all the packages you need.
4. In a code chunk, read in your dataset `diabetes.csv` and read the chunks for the two external files `exfile1.R` and `exfile2.R`.
5. Use the information in `exfile1.R` and `exfile2.R` to bring in the chunks corresponding to the Tables and Figure.  Note: you should not have any R code written in this file in the Tables and Figure section.
6. Set up the Introduction, Tables, and Figure sections.
7. Set up the Function section.  Hint: In the file `exfile1.R`, I've created an R object called `cat1`.  Use in-line text to include this picture in the output file. 

```{r data}
diabetes <- read.csv("diabetes.csv", stringsAsFactors = F)
read_chunk("exfile1.R")
read_chunk("exfile2.R")

```

```{r exfile1}
```

```{r exfile2}

```



#Introduction

The `diabetes` dataset has `r nrow(diabetes)` observations and `r ncol(diabetes)` variables. In this report, we create:

 1. A table displaying means and number of observations for the diabetes dataset as in Homework 1. 
 
 2. A table displaying the odds ratios for the diabetes dataset as in Lab 8.
 
 3. A plot displaying the odds ratios from Table 2 and corresponding 95% confidence intervals.

#Tables

```{r tabdiab}

```

```{r or_df}

```

#Figure
```{r figure, fig.cap = "Figure 1. Associations between covariates and diabetes", fig.width = 6, fig.height = 4}
```

# Functions

Cute cat function courtesy of Scott Chamberlain <http://rforcats.net/>.

```{r cat}
```

`r cat1`
