---
title: "Intro to R for Epidemiologists"
---




# Lab 11 (4/2/15)

For this lab, you will use R Markdown and `knitr` to recreate this report *exactly*, including this paragraph.  Specifically, use the `mtcars` dataset in R to recreate the **English text, table, and figure** you see here in an html file like this one.  Note: All the results printed in the "Introduction" section should be created using in-line R code.  Remember to:

- Use markdown to create headers, lists, bold, italics
- Name your code chunks
- Use code chunk options

## Introduction

The R dataset `mtcars` has `r length(mtcars)` variables and `r length(mtcars$am)` observations. The average fuel consumption reported was `r round(mean(mtcars$mpg),2)` mpg with a standard deviation of `r round(sd(mtcars$mpg),2)`. The average horsepower was `r round(mean(mtcars$hp),2)` (sd=`r round(sd(mtcars$hp),2)`).

In this report, we create:

1. A table displaying means for each variable by transmission type
2. A scatterplot of miles per gallon (MPG) and horsepower by transmission type

##Table
```{r setup, eval = T, echo = F, message = F, warning = F}
# Set working directory
setwd("~/Dropbox/IntrotoREpi/labs/week11")

# Load libraries
library(knitr)
library(tidyr)
library(dplyr)
library(ggplot2)

# Load data
data(mtcars)
```


```{r table, eval = T, echo = T}
# Make transmission a factor variable
mtcars$am <- factor(mtcars$am, levels = c(0,1), labels = c("automatic", 
  "manual"))
# Group data by transmission
gcars <- group_by(mtcars, am)
# Get means for each variable
t1 <- summarise_each(gcars, funs(mean(., na.rm = T)), mpg, disp : qsec)
# Print knitr table
kable(t1, digits = 2, 
  caption = "Means of Fuel Consumption and Auto Design Elements")
```


##Figure 
```{r plot, eval = T, echo = F}
# Set up ggplot
ggplot(mtcars, aes(x=hp, y=mpg, color=am)) + 
  # Add points
  geom_point(size=3.5,  alpha = I(0.5)) +
  # Add text
  xlab("Horsepower") + ylab("Miles per gallon (MPG)") + 
  ggtitle("MPG and Horsepower by Transmission Type") +
  # Change colors
  scale_color_manual(name = "", values=c("red", "blue"))
```
















