---
title: "Introduction to R for Epidemiologists"
author: "Jenna Krall, PhD"
date: "Thursday, April 9, 2015"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    theme: journal
    toc: yes
---


Last week:

- Introduction to knitr and markdown
- How to format text
- How to include code chunks
- In-line code
- Intro to code chunk options

Today:

*Note: you will need the `vlbw.csv` dataset for this lecture. 

- More markdown
- Header options
- More code chunk options

    - eval and echo
    - message and warning
    - global options
    - cache
- Figures in R Markdown

    - size
    - captions
    - alignment
    
- External code
- Output in PDF and Word
- Introduction to functions

# More markdown

Can also create linked urls: <http://jennakrall.com/IntrotoRepi/>

# Header options

## theme and highlight

## table of contents and numbered sections

# More code chunk options

## eval and echo

Recall: 

- eval = TRUE or FALSE depending on whether you want to run code
- echo = TRUE or FALSE depending on whether you want to show code

## message and warning



```{r dplyrmess, message = F}
library(dplyr)
```


In-class exercise 1: Change the knitr options for the code below to show only the plot.

```{r ggplotwarn, echo = F, warning = F}
library(ggplot2)
ggplot(data = airquality, aes(x = Temp, y = Ozone)) + geom_point()
```








## cache


```{r cache0, cache = T}
k <- 2
```

```{r cache1, cache = T, dependson = "cache0"}
seq1 <- seq(1, 100000)

minx <- vector()
for(i in 1 : k) {
    x <- sample(seq1, 1000)
    minx[i] <- min(x) 
}
print(length(minx))
```


## global options


I want to set eval = F and echo = F for all chunks

```{r knitr_options}
# Load knitr package
library(knitr)

# Set global options for echo, eval
opts_chunk$set(echo = T, eval = T, message = F, warning = F)

# Set directory for this file (only necessary if you want code to run somewhere other than where the file is located)
#opts_knit$set(root.dir = "~/Dropbox/IntrotoRepi/data")
```





# Figures

### size


```{r figunsize}
ggplot(data = airquality, aes(x = Temp, y = Ozone)) + geom_point()
```

```{r figsize, fig.height = 3, fig.width = 10}
ggplot(data = airquality, aes(x = Temp, y = Ozone)) + geom_point()
```


```{r figsizeout, out.width = "300px"}
ggplot(data = airquality, aes(x = Temp, y = Ozone)) + geom_point()
```

### captions



```{r figcap, fig.height = 3, fig.width = 3, fig.cap = "Figure 1. Plot of ozone vs. temperature"}
ggplot(data = airquality, aes(x = Temp, y = Ozone)) + geom_point()
```

### alignment


```{r figalleft, warning = F, fig.align = "left", fig.height = 3, fig.width = 3}
ggplot(data = airquality, aes(x = Temp, y = Ozone)) + geom_point()
```


```{r figalcenter, warning = F, fig.align = "center", fig.height = 3, fig.width = 3}
ggplot(data = airquality, aes(x = Temp, y = Ozone)) + geom_point()
```

# External code


## Source code

```{r src}
source("class_exfile1.R")
```

## Read chunk

```{r rchunk}
read_chunk("class_exfile1.R")
```
 
### Here is our figure

```{r g1, fig.cap = "Figure 1. Our first figure read externally"}
```

### Here is our table

To include captions, may need to specify `format = "pandoc"` in `kable()` and then specify `results = 'asis'` in the code chunk.

```{r tab1, results='asis'}
```


In-class exercise 2: Modify the file `class_exfile1.R` and this file to include a table of standard deviations similar to tab1.


```{r tab2, results='asis'}

```

# Output in PDF and Word

# Google maps in R markdown output

```{r beach, results = 'asis', eval = T}
library(googleVis)

# specify options
op <- options(gvis.plot.tag='chart')
# specify names
jensen <- data.frame(matrix(c("Jensen Beach, FL", "Jensen Beach"), nrow = 1))
colnames(jensen) <- c("loc", "tip")

# set up map
map1 <- gvisMap(jensen, "loc", "tip", options = list(zoomLevel = 5))
plot(map1)

```



# Introduction to functions

```{r myfun}
myfun(2, 3)
```


```{r ors}
vlbw <- read.csv("vlbw.csv")

#OR of dead comparing pneumo to not
ps <- tapply(vlbw$dead, vlbw$pneumo, mean, na.rm = T)
p_1 <- ps[2]
p_2 <- ps[1]
odds_1 <- p_1 / (1 - p_1)
odds_2 <- p_2 / (1 - p_2)
odds_1 / odds_2


```



In-class exercise 3: Write a function (orfun) to estimate the odds ratio from two vectors.  Assume x and y are 0 for unexposed/diseased, 1 for exposed/diseased

```{r ex3, eval = F}
orfun(vlbw$pneumo, vlbw$dead)
orfun(vlbw$twn, vlbw$dead)


library(epitools)
epitab(vlbw$dead, vlbw$pneumo)
epitab(vlbw$pneumo, vlbw$dead)
epitab(vlbw$twn, vlbw$dead)
```

