---
title: "Introduction to R for Epidemiologists"
author: "Jenna Krall"
date: "Thursday April 23, 2015"
output: html_document
---

```{r knitr_options, echo = F, message = F, warning = F}
# Load packages
library(knitr)
library(dplyr)
library(pander)
library(htmlTable)
library(ReporteRs)

# Set global options for echo, eval
opts_chunk$set(echo = T, eval = T, message = F, warning = F)

# Set directory for this file (only necessary if you want code to run somewhere other than where the file is located)
opts_knit$set(root.dir = "~/Dropbox/IntrotoRepi/data")
```

# Conditional formatting


## Example in rmarkdown using pander

- Useful for pandoc/markdown documents
- Only useful for bold/italicized formatting
- Can be converted to MS word
- Updated 2/20/15


### Custom highlighting

```{r}

# Load and organize data
load("tab_diab.RData")
tab_diab <- select(tab_diab, 1 , 7,  10)
tab_diab[, "Meandiff_Pval"] <- round(tab_diab[, "Meandiff_Pval"], 3)


# Create sequence of even rows
seqs1 <- seq(2, nrow(tab_diab), by = 2)
seqs1
# Add bold to rows
emphasize.strong.rows(seqs1)
# Show table
pander(tab_diab)

# Find row/col entries of significance
wh1 <- which(tab_diab < 0.05 & tab_diab >= 0, arr.ind = T)
wh1
# Add bold
emphasize.strong.cells(wh1)
pander(tab_diab)

# Add italicized
emphasize.cells(wh1)
pander(tab_diab)

```


### Better formatting for R output
```{r}
# Run standard linear model
glm1 <- lm(Ozone ~ Temp, data = airquality)
# Nice markdown output
pander(glm1)
pander(summary(glm1))
```



### Add significance stars

```{r}
# Resave output
tab_diab2 <- tab_diab
# Add stars to pvalue
tab_diab2[, "Meandiff_Pval"] <- add.significance.stars(tab_diab[, "Meandiff_Pval"])
pander(tab_diab2)
```



## Example in html using htmlTable

- Uses html formatting
- Can control row/column shading
- Updated 4/21/15
- Does **not** work with MS word 
- specify `results = "asis"`


### Row shading
```{r, results = "asis"}
# Get alternating row color shading
cols <- rep(c("white", "grey"), length = nrow(tab_diab))
# Get html table
h1 <- htmlTable(tab_diab, col.rgroup = cols)
h1
```



### Reformat pvalues

```{r}
tab_diab[, 3] <- txtPval(tab_diab[, 3])
h1 <- htmlTable(tab_diab, col.rgroup = cols)
h1

```



### Add more formatting
```{r}
# Define text colors for each cell
cols2 <- matrix(rep(c("color: #FF00FF;", "color: #6666FF;"), 
  length = nrow(tab_diab) *3), ncol = 3, byrow = F)
h1 <- htmlTable(tab_diab, css.cell = cols2)
h1

# Define cgroups
# Add alignment
# Add captions
h1 <- htmlTable(tab_diab, cgroup = c("name", "results"), n.cgroup = c(1, 2), 
  align.cgroup = "l", align = c("c", "l", "l"), col.columns = c("grey", 
  "white", "white"), caption = "Table 1. tab_diab", pos.caption = "bottom")
h1



```



## Example in Word using ReporteRs

- Does not work with `knitr`
- Creates MS word file
- Adds objects to file, including formatted tables


```{r}
# Create table
tabdiabFT <- FlexTable(tab_diab)
# Modify cell properties
tabdiabFT[seq(2, nrow(tab_diab), by = 2), ] <- cellProperties(background.color = "grey")

# Define output filename
doc.filename = "example_table.docx"
# Define docx
doc = docx( )
# Add table
doc = addFlexTable( doc, tabdiabFT )
# Write file
writeDoc( doc, file = doc.filename )
```
